---
dataMaid: yes
title: Codebook for Tidydata
subtitle: "Tidydata is a dataset that has been merged and pre-processed from raw data of Human Activity Recognition Using Smartphones Data Set"
date: 2021-06-30
output: pdf_document
geometry: margin=2cm
documentclass: article
header-includes:
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
  - \renewcommand\familydefault{\sfdefault}
  - \newcommand{\bminione}{\begin{minipage}{0.75 \textwidth}}
  - \newcommand{\bminitwo}{\begin{minipage}{0.25 \textwidth}}
  - \newcommand{\emini}{\end{minipage}}
---

```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library("ggplot2")
library("pander")
```

```{r 'visualFunctions', echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```

# Data report overview

The dataset examined has the following dimensions:

+------------------------+--------+
| Feature                | Result |
+:=======================+=======:+
| Number of observations | 10299  |
+------------------------+--------+
| Number of variables    | 82     |
+------------------------+--------+

# Data set information

Human Activity Recognition database built from the recordings of 30 subjects performing activities of daily living (ADL) while carrying a waist-mounted smartphone with embedded inertial sensors. More information of this data set can be found in this [page](the https://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones).

# Source Data

The source data can be obtained from [here](https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip) and comprises the following:

-   *features.txt:* list of feature names (measurement variables).

-   *activity_labels.txt:* list of descriptions of all activities (labels).

-   *X_train.txt:* training set.

-   *y_train.txt:* training labels.

-   *subject_train.txt:* each row identifies the subject who performed the activity in the training set.

-   *X_test.txt:* test set.

-   *y_test.txt:* test labels.

-   *subject_test.txt:* each row identifies the subject who performed the activity in the test set.

# Transformation steps to create Tidydata

The transformation steps to create Tidydata are recorded in *run_analysis.R*, and are described below:

1\\. **Merges the training and test sets to create one data set**

*X_train.txt*, *y_train.txt* and *subject_train.txt* were combined column-wise to create the training data set and *X_test.txt*, *y_test.txt* and *subject_test.txt* were combined column-wise to create the test data set.

The training and test data were combined row-wise to create the full data set.

2\\. **Appropriately labels the data set with descriptive variable names** (refer to CodeBook.md)

*features.txt* was used to label the measurement variables.

3\\. **Extracts only the variables that are mean and standard deviation for each measurement**

Only measurement variables containing mean() and std() in the variable names were retained.

4\\. **Applies descriptive activity names to name the activities in the data set**

*activity_labels.txt* was used to descriptively label the activities in the data set.

5\\. **Creates a second, independent tidy data set with the average of each variable for each activity and each subject**

Each variable was summarized by its mean by activity and subject using dplyr and stored in a text file *summarytidydata.txt*.

# Codebook summary table

+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
| Label | Variable                                                                                          | Class     | \# unique values | Missing | Description |
+:======+:==================================================================================================+:==========+=================:+:=======:+:============+
|       | [**label**]                                                                                       | integer   | 6                | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometer-mean()-X**](#timebodyaccelerometer-mean-x)                               | numeric   | 10292            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometer-mean()-Y**](#timebodyaccelerometer-mean-y)                               | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometer-mean()-Z**](#timebodyaccelerometer-mean-z)                               | numeric   | 10293            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometer-std()-X**](#timebodyaccelerometer-std-x)                                 | numeric   | 10295            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometer-std()-Y**](#timebodyaccelerometer-std-y)                                 | numeric   | 10297            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometer-std()-Z**](#timebodyaccelerometer-std-z)                                 | numeric   | 10297            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeGravityAccelerometer-mean()-X**](#timegravityaccelerometer-mean-x)                         | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeGravityAccelerometer-mean()-Y**](#timegravityaccelerometer-mean-y)                         | numeric   | 10298            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeGravityAccelerometer-mean()-Z**](#timegravityaccelerometer-mean-z)                         | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeGravityAccelerometer-std()-X**](#timegravityaccelerometer-std-x)                           | numeric   | 10288            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeGravityAccelerometer-std()-Y**](#timegravityaccelerometer-std-y)                           | numeric   | 10293            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeGravityAccelerometer-std()-Z**](#timegravityaccelerometer-std-z)                           | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometerJerk-mean()-X**](#timebodyaccelerometerjerk-mean-x)                       | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometerJerk-mean()-Y**](#timebodyaccelerometerjerk-mean-y)                       | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometerJerk-mean()-Z**](#timebodyaccelerometerjerk-mean-z)                       | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometerJerk-std()-X**](#timebodyaccelerometerjerk-std-x)                         | numeric   | 10290            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometerJerk-std()-Y**](#timebodyaccelerometerjerk-std-y)                         | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometerJerk-std()-Z**](#timebodyaccelerometerjerk-std-z)                         | numeric   | 10293            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscope-mean()-X**](#timebodygyroscope-mean-x)                                       | numeric   | 10298            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscope-mean()-Y**](#timebodygyroscope-mean-y)                                       | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscope-mean()-Z**](#timebodygyroscope-mean-z)                                       | numeric   | 10297            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscope-std()-X**](#timebodygyroscope-std-x)                                         | numeric   | 10292            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscope-std()-Y**](#timebodygyroscope-std-y)                                         | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscope-std()-Z**](#timebodygyroscope-std-z)                                         | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscopeJerk-mean()-X**](#timebodygyroscopejerk-mean-x)                               | numeric   | 10295            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscopeJerk-mean()-Y**](#timebodygyroscopejerk-mean-y)                               | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscopeJerk-mean()-Z**](#timebodygyroscopejerk-mean-z)                               | numeric   | 10298            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscopeJerk-std()-X**](#timebodygyroscopejerk-std-x)                                 | numeric   | 10292            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscopeJerk-std()-Y**](#timebodygyroscopejerk-std-y)                                 | numeric   | 10295            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscopeJerk-std()-Z**](#timebodygyroscopejerk-std-z)                                 | numeric   | 10291            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometerMagnitude-mean()**](#timebodyaccelerometermagnitude-mean)                 | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometerMagnitude-std()**](#timebodyaccelerometermagnitude-std)                   | numeric   | 10294            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeGravityAccelerometerMagnitude-mean()**](#timegravityaccelerometermagnitude-mean)           | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeGravityAccelerometerMagnitude-std()**](#timegravityaccelerometermagnitude-std)             | numeric   | 10294            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometerJerkMagnitude-mean()**](#timebodyaccelerometerjerkmagnitude-mean)         | numeric   | 10292            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyAccelerometerJerkMagnitude-std()**](#timebodyaccelerometerjerkmagnitude-std)           | numeric   | 10294            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscopeMagnitude-mean()**](#timebodygyroscopemagnitude-mean)                         | numeric   | 10298            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscopeMagnitude-std()**](#timebodygyroscopemagnitude-std)                           | numeric   | 10298            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscopeJerkMagnitude-mean()**](#timebodygyroscopejerkmagnitude-mean)                 | numeric   | 10293            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**timeBodyGyroscopeJerkMagnitude-std()**](#timebodygyroscopejerkmagnitude-std)                   | numeric   | 10297            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometer-mean()-X**](#freqbodyaccelerometer-mean-x)                               | numeric   | 10295            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometer-mean()-Y**](#freqbodyaccelerometer-mean-y)                               | numeric   | 10292            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometer-mean()-Z**](#freqbodyaccelerometer-mean-z)                               | numeric   | 10295            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometer-std()-X**](#freqbodyaccelerometer-std-x)                                 | numeric   | 10294            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometer-std()-Y**](#freqbodyaccelerometer-std-y)                                 | numeric   | 10297            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometer-std()-Z**](#freqbodyaccelerometer-std-z)                                 | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometer-meanFreq()-X**](#freqbodyaccelerometer-meanfreq-x)                       | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometer-meanFreq()-Y**](#freqbodyaccelerometer-meanfreq-y)                       | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometer-meanFreq()-Z**](#freqbodyaccelerometer-meanfreq-z)                       | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerJerk-mean()-X**](#freqbodyaccelerometerjerk-mean-x)                       | numeric   | 10293            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerJerk-mean()-Y**](#freqbodyaccelerometerjerk-mean-y)                       | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerJerk-mean()-Z**](#freqbodyaccelerometerjerk-mean-z)                       | numeric   | 10294            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerJerk-std()-X**](#freqbodyaccelerometerjerk-std-x)                         | numeric   | 10291            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerJerk-std()-Y**](#freqbodyaccelerometerjerk-std-y)                         | numeric   | 10294            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerJerk-std()-Z**](#freqbodyaccelerometerjerk-std-z)                         | numeric   | 10290            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerJerk-meanFreq()-X**](#freqbodyaccelerometerjerk-meanfreq-x)               | numeric   | 10298            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerJerk-meanFreq()-Y**](#freqbodyaccelerometerjerk-meanfreq-y)               | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerJerk-meanFreq()-Z**](#freqbodyaccelerometerjerk-meanfreq-z)               | numeric   | 10298            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscope-mean()-X**](#freqbodygyroscope-mean-x)                                       | numeric   | 10297            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscope-mean()-Y**](#freqbodygyroscope-mean-y)                                       | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscope-mean()-Z**](#freqbodygyroscope-mean-z)                                       | numeric   | 10297            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscope-std()-X**](#freqbodygyroscope-std-x)                                         | numeric   | 10297            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscope-std()-Y**](#freqbodygyroscope-std-y)                                         | numeric   | 10293            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscope-std()-Z**](#freqbodygyroscope-std-z)                                         | numeric   | 10295            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscope-meanFreq()-X**](#freqbodygyroscope-meanfreq-x)                               | numeric   | 10298            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscope-meanFreq()-Y**](#freqbodygyroscope-meanfreq-y)                               | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscope-meanFreq()-Z**](#freqbodygyroscope-meanfreq-z)                               | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerMagnitude-mean()**](#freqbodyaccelerometermagnitude-mean)                 | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerMagnitude-std()**](#freqbodyaccelerometermagnitude-std)                   | numeric   | 10298            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerMagnitude-meanFreq()**](#freqbodyaccelerometermagnitude-meanfreq)         | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerJerkMagnitude-mean()**](#freqbodyaccelerometerjerkmagnitude-mean)         | numeric   | 10290            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerJerkMagnitude-std()**](#freqbodyaccelerometerjerkmagnitude-std)           | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyAccelerometerJerkMagnitude-meanFreq()**](#freqbodyaccelerometerjerkmagnitude-meanfreq) | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscopeMagnitude-mean()**](#freqbodygyroscopemagnitude-mean)                         | numeric   | 10297            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscopeMagnitude-std()**](#freqbodygyroscopemagnitude-std)                           | numeric   | 10296            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscopeMagnitude-meanFreq()**](#freqbodygyroscopemagnitude-meanfreq)                 | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscopeJerkMagnitude-mean()**](#freqbodygyroscopejerkmagnitude-mean)                 | numeric   | 10293            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscopeJerkMagnitude-std()**](#freqbodygyroscopejerkmagnitude-std)                   | numeric   | 10292            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**freqBodyGyroscopeJerkMagnitude-meanFreq()**](#freqbodygyroscopejerkmagnitude-meanfreq)         | numeric   | 10299            | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**subject**]                                                                                     | integer   | 30               | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+
|       | [**activity**]                                                                                    | character | 6                | 0.00 %  |             |
+-------+---------------------------------------------------------------------------------------------------+-----------+------------------+---------+-------------+

# Variable list

## label

\bminione

+-------------------------+---------+
| Feature                 | Result  |
+:========================+========:+
| Variable type           | integer |
+-------------------------+---------+
| Number of missing obs.  | 0 (0 %) |
+-------------------------+---------+
| Number of unique values | 6       |
+-------------------------+---------+
| Median                  | 4       |
+-------------------------+---------+
| 1st and 3rd quartiles   | 2; 5    |
+-------------------------+---------+
| Min. and max.           | 1; 6    |
+-------------------------+---------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-1-label', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.5, 2, 2.5, 3, 3.5, 
4, 4.5, 5, 5.5), xmax = c(1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, 5.5, 
6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1722L, 1544L, 
0L, 1406L, 0L, 1777L, 0L, 1906L, 0L, 1944L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "label")
```

\emini

\fullline

## timeBodyAccelerometer-mean()-X {#timebodyaccelerometer-mean-x}

\bminione

+-------------------------+------------+
| Feature                 | Result     |
+:========================+===========:+
| Variable type           | numeric    |
+-------------------------+------------+
| Number of missing obs.  | 0 (0 %)    |
+-------------------------+------------+
| Number of unique values | 10292      |
+-------------------------+------------+
| Median                  | 0.28       |
+-------------------------+------------+
| 1st and 3rd quartiles   | 0.26; 0.29 |
+-------------------------+------------+
| Min. and max.           | -1; 1      |
+-------------------------+------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-2-timeBodyAccelerometer-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 2L, 0L, 0L, 3L, 7L, 4L, 5L, 8L, 
17L, 72L, 643L, 7579L, 1679L, 257L, 14L, 7L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "timeBodyAccelerometer-mean()-X")
```

\emini

\fullline

## timeBodyAccelerometer-mean()-Y {#timebodyaccelerometer-mean-y}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10299        |
+-------------------------+--------------+
| Median                  | -0.02        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.02; -0.01 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-3-timeBodyAccelerometer-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 0L, 0L, 3L, 3L, 3L, 2L, 4L, 90L, 
8855L, 1283L, 30L, 15L, 5L, 1L, 2L, 1L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "timeBodyAccelerometer-mean()-Y")
```

\emini

\fullline

## timeBodyAccelerometer-mean()-Z {#timebodyaccelerometer-mean-z}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10293       |
+-------------------------+-------------+
| Median                  | -0.11       |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.12; -0.1 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-4-timeBodyAccelerometer-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(2L, 1L, 1L, 0L, 8L, 9L, 29L, 218L, 7132L, 
2742L, 111L, 25L, 8L, 7L, 1L, 1L, 0L, 1L, 1L, 2L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "timeBodyAccelerometer-mean()-Z")
```

\emini

\fullline

## timeBodyAccelerometer-std()-X {#timebodyaccelerometer-std-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10295        |
+-------------------------+--------------+
| Median                  | -0.94        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.25 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-5-timeBodyAccelerometer-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5407L, 141L, 40L, 64L, 106L, 537L, 970L, 
872L, 580L, 479L, 349L, 292L, 208L, 140L, 69L, 20L, 11L, 9L, 
4L, 1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyAccelerometer-std()-X")
```

\emini

\fullline

## timeBodyAccelerometer-std()-Y {#timebodyaccelerometer-std-y}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10297        |
+-------------------------+--------------+
| Median                  | -0.84        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.06 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-6-timeBodyAccelerometer-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4774L, 482L, 162L, 87L, 44L, 60L, 208L, 
579L, 960L, 838L, 724L, 519L, 349L, 250L, 125L, 62L, 38L, 17L, 
12L, 9L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyAccelerometer-std()-Y")
```

\emini

\fullline

## timeBodyAccelerometer-std()-Z {#timebodyaccelerometer-std-z}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10297        |
+-------------------------+--------------+
| Median                  | -0.85        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.28 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-7-timeBodyAccelerometer-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4881L, 420L, 143L, 133L, 323L, 650L, 
965L, 963L, 624L, 422L, 288L, 213L, 116L, 60L, 37L, 21L, 18L, 
14L, 5L, 3L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "timeBodyAccelerometer-std()-Z")
```

\emini

\fullline

## timeGravityAccelerometer-mean()-X {#timegravityaccelerometer-mean-x}

\bminione

+-------------------------+------------+
| Feature                 | Result     |
+:========================+===========:+
| Variable type           | numeric    |
+-------------------------+------------+
| Number of missing obs.  | 0 (0 %)    |
+-------------------------+------------+
| Number of unique values | 10296      |
+-------------------------+------------+
| Median                  | 0.92       |
+-------------------------+------------+
| 1st and 3rd quartiles   | 0.81; 0.95 |
+-------------------------+------------+
| Min. and max.           | -1; 1      |
+-------------------------+------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-8-timeGravityAccelerometer-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(24L, 24L, 82L, 83L, 247L, 392L, 322L, 
413L, 273L, 80L, 2L, 16L, 1L, 24L, 17L, 17L, 151L, 319L, 1650L, 
6162L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeGravityAccelerometer-mean()-X")
```

\emini

\fullline

## timeGravityAccelerometer-mean()-Y {#timegravityaccelerometer-mean-y}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10298       |
+-------------------------+-------------+
| Median                  | -0.14       |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.24; 0.12 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-9-timeGravityAccelerometer-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(27L, 0L, 0L, 0L, 35L, 301L, 1141L, 2311L, 
2075L, 1078L, 659L, 367L, 273L, 192L, 274L, 306L, 205L, 354L, 
309L, 392L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "timeGravityAccelerometer-mean()-Y")
```

\emini

\fullline

## timeGravityAccelerometer-mean()-Z {#timegravityaccelerometer-mean-z}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10299       |
+-------------------------+-------------+
| Median                  | 0.04        |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.12; 0.22 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-10-timeGravityAccelerometer-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(52L, 1L, 0L, 2L, 51L, 213L, 500L, 801L, 
1180L, 1551L, 2077L, 1210L, 614L, 409L, 254L, 205L, 364L, 191L, 
387L, 237L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "timeGravityAccelerometer-mean()-Z")
```

\emini

\fullline

## timeGravityAccelerometer-std()-X {#timegravityaccelerometer-std-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10288        |
+-------------------------+--------------+
| Median                  | -0.98        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.96 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-11-timeGravityAccelerometer-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(9719L, 401L, 84L, 22L, 24L, 10L, 14L, 
6L, 5L, 1L, 1L, 1L, 3L, 2L, 1L, 2L, 1L, 1L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "timeGravityAccelerometer-std()-X")
```

\emini

\fullline

## timeGravityAccelerometer-std()-Y {#timegravityaccelerometer-std-y}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10293        |
+-------------------------+--------------+
| Median                  | -0.98        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.95 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-12-timeGravityAccelerometer-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(9334L, 692L, 127L, 65L, 20L, 6L, 17L, 
11L, 10L, 4L, 5L, 1L, 2L, 0L, 1L, 0L, 1L, 1L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "timeGravityAccelerometer-std()-Y")
```

\emini

\fullline

## timeGravityAccelerometer-std()-Z {#timegravityaccelerometer-std-z}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10296        |
+-------------------------+--------------+
| Median                  | -0.97        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.93 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-13-timeGravityAccelerometer-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(8695L, 1101L, 261L, 108L, 42L, 30L, 
18L, 11L, 5L, 6L, 6L, 3L, 2L, 3L, 2L, 3L, 0L, 1L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "timeGravityAccelerometer-std()-Z")
```

\emini

\fullline

## timeBodyAccelerometerJerk-mean()-X {#timebodyaccelerometerjerk-mean-x}

\bminione

+-------------------------+------------+
| Feature                 | Result     |
+:========================+===========:+
| Variable type           | numeric    |
+-------------------------+------------+
| Number of missing obs.  | 0 (0 %)    |
+-------------------------+------------+
| Number of unique values | 10299      |
+-------------------------+------------+
| Median                  | 0.08       |
+-------------------------+------------+
| 1st and 3rd quartiles   | 0.06; 0.09 |
+-------------------------+------------+
| Min. and max.           | -1; 1      |
+-------------------------+------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-14-timeBodyAccelerometerJerk-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 2L, 12L, 16L, 46L, 78L, 169L, 280L, 
435L, 691L, 6179L, 959L, 591L, 336L, 242L, 127L, 62L, 44L, 23L, 
6L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyAccelerometerJerk-mean()-X")
```

\emini

\fullline

## timeBodyAccelerometerJerk-mean()-Y {#timebodyaccelerometerjerk-mean-y}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10299       |
+-------------------------+-------------+
| Median                  | 0.01        |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.02; 0.03 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-15-timeBodyAccelerometerJerk-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4L, 5L, 13L, 15L, 60L, 111L, 232L, 411L, 
670L, 1767L, 5405L, 699L, 433L, 233L, 119L, 67L, 36L, 9L, 7L, 
3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyAccelerometerJerk-mean()-Y")
```

\emini

\fullline

## timeBodyAccelerometerJerk-mean()-Z {#timebodyaccelerometerjerk-mean-z}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10299       |
+-------------------------+-------------+
| Median                  | 0           |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.03; 0.02 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-16-timeBodyAccelerometerJerk-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(3L, 9L, 8L, 18L, 51L, 120L, 222L, 440L, 
727L, 3775L, 3509L, 662L, 357L, 214L, 101L, 43L, 22L, 11L, 6L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyAccelerometerJerk-mean()-Z")
```

\emini

\fullline

## timeBodyAccelerometerJerk-std()-X {#timebodyaccelerometerjerk-std-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10290        |
+-------------------------+--------------+
| Median                  | -0.95        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.29 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-17-timeBodyAccelerometerJerk-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5526L, 88L, 38L, 129L, 342L, 689L, 840L, 
744L, 592L, 501L, 351L, 249L, 102L, 53L, 23L, 15L, 10L, 5L, 0L, 
2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyAccelerometerJerk-std()-X")
```

\emini

\fullline

## timeBodyAccelerometerJerk-std()-Y {#timebodyaccelerometerjerk-std-y}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10296        |
+-------------------------+--------------+
| Median                  | -0.93        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.22 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-18-timeBodyAccelerometerJerk-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5353L, 224L, 60L, 119L, 271L, 472L, 
685L, 696L, 698L, 647L, 424L, 281L, 176L, 90L, 53L, 33L, 8L, 
6L, 2L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "timeBodyAccelerometerJerk-std()-Y")
```

\emini

\fullline

## timeBodyAccelerometerJerk-std()-Z {#timebodyaccelerometerjerk-std-z}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10293        |
+-------------------------+--------------+
| Median                  | -0.95        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.55 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-19-timeBodyAccelerometerJerk-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5524L, 220L, 632L, 933L, 917L, 849L, 
547L, 284L, 158L, 101L, 74L, 28L, 16L, 8L, 5L, 1L, 0L, 0L, 1L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyAccelerometerJerk-std()-Z")
```

\emini

\fullline

## timeBodyGyroscope-mean()-X {#timebodygyroscope-mean-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10298        |
+-------------------------+--------------+
| Median                  | -0.03        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.05; -0.01 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-20-timeBodyGyroscope-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(2L, 6L, 19L, 78L, 138L, 254L, 305L, 
312L, 536L, 6405L, 1013L, 363L, 255L, 304L, 212L, 74L, 18L, 4L, 
0L, 1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscope-mean()-X")
```

\emini

\fullline

## timeBodyGyroscope-mean()-Y {#timebodygyroscope-mean-y}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10299       |
+-------------------------+-------------+
| Median                  | -0.07       |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.1; -0.05 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-21-timeBodyGyroscope-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(2L, 1L, 8L, 21L, 58L, 132L, 286L, 568L, 
1640L, 5994L, 820L, 394L, 214L, 89L, 44L, 15L, 9L, 3L, 0L, 1L
)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscope-mean()-Y")
```

\emini

\fullline

## timeBodyGyroscope-mean()-Z {#timebodygyroscope-mean-z}

\bminione

+-------------------------+------------+
| Feature                 | Result     |
+:========================+===========:+
| Variable type           | numeric    |
+-------------------------+------------+
| Number of missing obs.  | 0 (0 %)    |
+-------------------------+------------+
| Number of unique values | 10297      |
+-------------------------+------------+
| Median                  | 0.09       |
+-------------------------+------------+
| 1st and 3rd quartiles   | 0.06; 0.11 |
+-------------------------+------------+
| Min. and max.           | -1; 1      |
+-------------------------+------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-22-timeBodyGyroscope-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(2L, 5L, 6L, 7L, 26L, 42L, 79L, 125L, 
227L, 614L, 6051L, 2154L, 457L, 230L, 126L, 64L, 46L, 26L, 6L, 
6L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscope-mean()-Z")
```

\emini

\fullline

## timeBodyGyroscope-std()-X {#timebodygyroscope-std-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10292        |
+-------------------------+--------------+
| Median                  | -0.9         |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.48 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-23-timeBodyGyroscope-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5156L, 328L, 263L, 711L, 1083L, 985L, 
737L, 460L, 281L, 162L, 65L, 34L, 12L, 6L, 9L, 5L, 0L, 0L, 1L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscope-std()-X")
```

\emini

\fullline

## timeBodyGyroscope-std()-Y {#timebodygyroscope-std-y}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10296        |
+-------------------------+--------------+
| Median                  | -0.91        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.45 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-24-timeBodyGyroscope-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5232L, 302L, 115L, 509L, 1052L, 882L, 
593L, 438L, 344L, 283L, 258L, 115L, 54L, 48L, 33L, 20L, 15L, 
1L, 2L, 3L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "timeBodyGyroscope-std()-Y")
```

\emini

\fullline

## timeBodyGyroscope-std()-Z {#timebodygyroscope-std-z}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10296        |
+-------------------------+--------------+
| Median                  | -0.88        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.34 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-25-timeBodyGyroscope-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5003L, 488L, 128L, 200L, 458L, 790L, 
1038L, 902L, 593L, 301L, 129L, 87L, 56L, 34L, 29L, 28L, 11L, 
11L, 7L, 6L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "timeBodyGyroscope-std()-Z")
```

\emini

\fullline

## timeBodyGyroscopeJerk-mean()-X {#timebodygyroscopejerk-mean-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10295        |
+-------------------------+--------------+
| Median                  | -0.1         |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.12; -0.08 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-26-timeBodyGyroscopeJerk-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(3L, 1L, 10L, 17L, 57L, 151L, 310L, 736L, 
2950L, 4684L, 744L, 388L, 150L, 52L, 25L, 12L, 7L, 0L, 1L, 1L
)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscopeJerk-mean()-X")
```

\emini

\fullline

## timeBodyGyroscopeJerk-mean()-Y {#timebodygyroscopejerk-mean-y}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10299        |
+-------------------------+--------------+
| Median                  | -0.04        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.06; -0.03 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-27-timeBodyGyroscopeJerk-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 2L, 3L, 14L, 25L, 42L, 170L, 431L, 
997L, 6770L, 1088L, 458L, 172L, 74L, 32L, 10L, 6L, 2L, 1L, 1L
)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscopeJerk-mean()-Y")
```

\emini

\fullline

## timeBodyGyroscopeJerk-mean()-Z {#timebodygyroscopejerk-mean-z}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10298        |
+-------------------------+--------------+
| Median                  | -0.05        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.08; -0.03 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-28-timeBodyGyroscopeJerk-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 6L, 6L, 13L, 40L, 98L, 223L, 540L, 
1158L, 6277L, 1104L, 485L, 195L, 90L, 35L, 18L, 4L, 2L, 3L, 1L
)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscopeJerk-mean()-Z")
```

\emini

\fullline

## timeBodyGyroscopeJerk-std()-X {#timebodygyroscopejerk-std-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10292        |
+-------------------------+--------------+
| Median                  | -0.93        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.49 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-29-timeBodyGyroscopeJerk-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5391L, 206L, 309L, 738L, 955L, 994L, 
699L, 474L, 238L, 130L, 76L, 41L, 22L, 12L, 5L, 4L, 2L, 0L, 2L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscopeJerk-std()-X")
```

\emini

\fullline

## timeBodyGyroscopeJerk-std()-Y {#timebodygyroscopejerk-std-y}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10295        |
+-------------------------+--------------+
| Median                  | -0.95        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.63 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-30-timeBodyGyroscopeJerk-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5522L, 554L, 934L, 967L, 834L, 557L, 
341L, 183L, 124L, 104L, 56L, 44L, 22L, 24L, 14L, 8L, 4L, 4L, 
1L, 2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscopeJerk-std()-Y")
```

\emini

\fullline

## timeBodyGyroscopeJerk-std()-Z {#timebodygyroscopejerk-std-z}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10291        |
+-------------------------+--------------+
| Median                  | -0.95        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.51 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-31-timeBodyGyroscopeJerk-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5511L, 116L, 337L, 774L, 1088L, 924L, 
645L, 377L, 212L, 130L, 74L, 50L, 32L, 9L, 13L, 5L, 0L, 0L, 0L, 
2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscopeJerk-std()-Z")
```

\emini

\fullline

## timeBodyAccelerometerMagnitude-mean() {#timebodyaccelerometermagnitude-mean}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10296        |
+-------------------------+--------------+
| Median                  | -0.87        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.12 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-32-timeBodyAccelerometerMagnitude-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5016L, 356L, 110L, 51L, 27L, 84L, 347L, 
893L, 1058L, 821L, 551L, 477L, 286L, 144L, 41L, 11L, 7L, 13L, 
3L, 3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyAccelerometerMagnitude-mean()")
```

\emini

\fullline

## timeBodyAccelerometerMagnitude-std() {#timebodyaccelerometermagnitude-std}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10294        |
+-------------------------+--------------+
| Median                  | -0.84        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.24 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-33-timeBodyAccelerometerMagnitude-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4865L, 407L, 143L, 81L, 276L, 648L, 
804L, 862L, 676L, 383L, 341L, 329L, 236L, 145L, 62L, 26L, 6L, 
5L, 3L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "timeBodyAccelerometerMagnitude-std()")
```

\emini

\fullline

## timeGravityAccelerometerMagnitude-mean() {#timegravityaccelerometermagnitude-mean}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10296        |
+-------------------------+--------------+
| Median                  | -0.87        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.12 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-34-timeGravityAccelerometerMagnitude-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5016L, 356L, 110L, 51L, 27L, 84L, 347L, 
893L, 1058L, 821L, 551L, 477L, 286L, 144L, 41L, 11L, 7L, 13L, 
3L, 3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeGravityAccelerometerMagnitude-mean()")
```

\emini

\fullline

## timeGravityAccelerometerMagnitude-std() {#timegravityaccelerometermagnitude-std}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10294        |
+-------------------------+--------------+
| Median                  | -0.84        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.24 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-35-timeGravityAccelerometerMagnitude-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4865L, 407L, 143L, 81L, 276L, 648L, 
804L, 862L, 676L, 383L, 341L, 329L, 236L, 145L, 62L, 26L, 6L, 
5L, 3L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "timeGravityAccelerometerMagnitude-std()")
```

\emini

\fullline

## timeBodyAccelerometerJerkMagnitude-mean() {#timebodyaccelerometerjerkmagnitude-mean}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10292       |
+-------------------------+-------------+
| Median                  | -0.95       |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.99; -0.3 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-36-timeBodyAccelerometerJerkMagnitude-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5508L, 107L, 42L, 109L, 328L, 711L, 
872L, 844L, 755L, 531L, 249L, 124L, 58L, 32L, 10L, 10L, 3L, 3L, 
1L, 2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyAccelerometerJerkMagnitude-mean()")
```

\emini

\fullline

## timeBodyAccelerometerJerkMagnitude-std() {#timebodyaccelerometerjerkmagnitude-std}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10294        |
+-------------------------+--------------+
| Median                  | -0.93        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.27 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-37-timeBodyAccelerometerJerkMagnitude-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5349L, 223L, 73L, 105L, 359L, 699L, 
732L, 690L, 583L, 565L, 381L, 274L, 113L, 85L, 29L, 21L, 8L, 
7L, 2L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "timeBodyAccelerometerJerkMagnitude-std()")
```

\emini

\fullline

## timeBodyGyroscopeMagnitude-mean() {#timebodygyroscopemagnitude-mean}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10298        |
+-------------------------+--------------+
| Median                  | -0.82        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.25 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-38-timeBodyGyroscopeMagnitude-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4702L, 534L, 199L, 132L, 193L, 623L, 
842L, 963L, 837L, 556L, 342L, 184L, 91L, 50L, 28L, 10L, 4L, 5L, 
2L, 2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscopeMagnitude-mean()")
```

\emini

\fullline

## timeBodyGyroscopeMagnitude-std() {#timebodygyroscopemagnitude-std}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10298        |
+-------------------------+--------------+
| Median                  | -0.83        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.39 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-39-timeBodyGyroscopeMagnitude-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4607L, 657L, 252L, 407L, 831L, 920L, 
801L, 670L, 460L, 286L, 155L, 103L, 62L, 31L, 27L, 19L, 4L, 3L, 
2L, 2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscopeMagnitude-std()")
```

\emini

\fullline

## timeBodyGyroscopeJerkMagnitude-mean() {#timebodygyroscopejerkmagnitude-mean}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10293        |
+-------------------------+--------------+
| Median                  | -0.96        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.55 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-40-timeBodyGyroscopeJerkMagnitude-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5528L, 129L, 450L, 1097L, 1038L, 903L, 
501L, 304L, 155L, 80L, 54L, 30L, 13L, 9L, 5L, 1L, 0L, 0L, 1L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscopeJerkMagnitude-mean()")
```

\emini

\fullline

## timeBodyGyroscopeJerkMagnitude-std() {#timebodygyroscopejerkmagnitude-std}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10297        |
+-------------------------+--------------+
| Median                  | -0.94        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.61 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-41-timeBodyGyroscopeJerkMagnitude-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5414L, 405L, 890L, 1126L, 943L, 618L, 
304L, 191L, 130L, 90L, 66L, 51L, 31L, 17L, 7L, 7L, 4L, 2L, 2L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "timeBodyGyroscopeJerkMagnitude-std()")
```

\emini

\fullline

## freqBodyAccelerometer-mean()-X {#freqbodyaccelerometer-mean-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10295        |
+-------------------------+--------------+
| Median                  | -0.95        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.26 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-42-freqBodyAccelerometer-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5422L, 136L, 39L, 83L, 202L, 639L, 908L, 
798L, 654L, 459L, 370L, 296L, 161L, 76L, 28L, 12L, 6L, 7L, 2L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometer-mean()-X")
```

\emini

\fullline

## freqBodyAccelerometer-mean()-Y {#freqbodyaccelerometer-mean-y}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10292       |
+-------------------------+-------------+
| Median                  | -0.86       |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.98; -0.1 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-43-freqBodyAccelerometer-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4912L, 462L, 126L, 53L, 50L, 150L, 395L, 
755L, 849L, 758L, 619L, 478L, 311L, 172L, 96L, 48L, 37L, 15L, 
7L, 6L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometer-mean()-Y")
```

\emini

\fullline

## freqBodyAccelerometer-mean()-Z {#freqbodyaccelerometer-mean-z}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10295        |
+-------------------------+--------------+
| Median                  | -0.9         |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.37 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-44-freqBodyAccelerometer-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5106L, 335L, 102L, 332L, 605L, 891L, 
1028L, 780L, 441L, 238L, 187L, 105L, 66L, 37L, 22L, 13L, 6L, 
2L, 2L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyAccelerometer-mean()-Z")
```

\emini

\fullline

## freqBodyAccelerometer-std()-X {#freqbodyaccelerometer-std-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10294        |
+-------------------------+--------------+
| Median                  | -0.94        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.25 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-45-freqBodyAccelerometer-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5411L, 130L, 44L, 56L, 124L, 524L, 966L, 
805L, 623L, 459L, 369L, 247L, 213L, 156L, 82L, 55L, 19L, 8L, 
3L, 5L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometer-std()-X")
```

\emini

\fullline

## freqBodyAccelerometer-std()-Y {#freqbodyaccelerometer-std-y}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10297        |
+-------------------------+--------------+
| Median                  | -0.83        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.09 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-46-freqBodyAccelerometer-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4776L, 467L, 170L, 84L, 49L, 104L, 344L, 
737L, 916L, 882L, 656L, 441L, 289L, 191L, 93L, 51L, 24L, 13L, 
9L, 3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometer-std()-Y")
```

\emini

\fullline

## freqBodyAccelerometer-std()-Z {#freqbodyaccelerometer-std-z}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10296       |
+-------------------------+-------------+
| Median                  | -0.84       |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.98; -0.3 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-47-freqBodyAccelerometer-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4842L, 425L, 163L, 167L, 360L, 782L, 
1000L, 848L, 539L, 372L, 304L, 236L, 118L, 44L, 30L, 16L, 24L, 
14L, 11L, 4L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyAccelerometer-std()-Z")
```

\emini

\fullline

## freqBodyAccelerometer-meanFreq()-X {#freqbodyaccelerometer-meanfreq-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10299        |
+-------------------------+--------------+
| Median                  | -0.24        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.42; -0.02 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-48-freqBodyAccelerometer-meanFreq()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(25L, 65L, 152L, 438L, 838L, 1317L, 1492L, 
1368L, 1154L, 1101L, 1080L, 687L, 356L, 143L, 61L, 12L, 7L, 1L, 
0L, 2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometer-meanFreq()-X")
```

\emini

\fullline

## freqBodyAccelerometer-meanFreq()-Y {#freqbodyaccelerometer-meanfreq-y}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10299       |
+-------------------------+-------------+
| Median                  | 0           |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.14; 0.18 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-49-freqBodyAccelerometer-meanFreq()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 2L, 14L, 35L, 111L, 234L, 525L, 
925L, 1394L, 1843L, 1637L, 1264L, 1034L, 661L, 359L, 176L, 57L, 
19L, 4L, 4L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyAccelerometer-meanFreq()-Y")
```

\emini

\fullline

## freqBodyAccelerometer-meanFreq()-Z {#freqbodyaccelerometer-meanfreq-z}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10299       |
+-------------------------+-------------+
| Median                  | 0.06        |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.14; 0.25 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-50-freqBodyAccelerometer-meanFreq()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(9L, 18L, 38L, 96L, 195L, 317L, 509L, 
748L, 1119L, 1303L, 1361L, 1410L, 1206L, 947L, 572L, 259L, 123L, 
38L, 22L, 9L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyAccelerometer-meanFreq()-Z")
```

\emini

\fullline

## freqBodyAccelerometerJerk-mean()-X {#freqbodyaccelerometerjerk-mean-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10293        |
+-------------------------+--------------+
| Median                  | -0.95        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.33 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-51-freqBodyAccelerometerJerk-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5526L, 88L, 43L, 189L, 448L, 777L, 888L, 
728L, 552L, 416L, 322L, 155L, 86L, 39L, 17L, 13L, 9L, 2L, 0L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometerJerk-mean()-X")
```

\emini

\fullline

## freqBodyAccelerometerJerk-mean()-Y {#freqbodyaccelerometerjerk-mean-y}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10296        |
+-------------------------+--------------+
| Median                  | -0.93        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.26 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-52-freqBodyAccelerometerJerk-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5366L, 212L, 68L, 143L, 313L, 620L, 
727L, 790L, 731L, 519L, 363L, 234L, 91L, 63L, 37L, 11L, 7L, 3L, 
0L, 1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometerJerk-mean()-Y")
```

\emini

\fullline

## freqBodyAccelerometerJerk-mean()-Z {#freqbodyaccelerometerjerk-mean-z}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10294        |
+-------------------------+--------------+
| Median                  | -0.95        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.51 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-53-freqBodyAccelerometerJerk-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5497L, 186L, 483L, 854L, 827L, 937L, 
626L, 358L, 229L, 112L, 77L, 56L, 23L, 13L, 12L, 4L, 2L, 2L, 
0L, 1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometerJerk-mean()-Z")
```

\emini

\fullline

## freqBodyAccelerometerJerk-std()-X {#freqbodyaccelerometerjerk-std-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10291        |
+-------------------------+--------------+
| Median                  | -0.96        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.32 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-54-freqBodyAccelerometerJerk-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5543L, 79L, 44L, 176L, 435L, 755L, 857L, 
713L, 613L, 420L, 321L, 176L, 93L, 37L, 20L, 8L, 5L, 1L, 1L, 
2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometerJerk-std()-X")
```

\emini

\fullline

## freqBodyAccelerometerJerk-std()-Y {#freqbodyaccelerometerjerk-std-y}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10294        |
+-------------------------+--------------+
| Median                  | -0.93        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.24 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-55-freqBodyAccelerometerJerk-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5370L, 220L, 58L, 144L, 297L, 502L, 
693L, 689L, 641L, 582L, 449L, 266L, 162L, 97L, 70L, 34L, 15L, 
6L, 2L, 2L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyAccelerometerJerk-std()-Y")
```

\emini

\fullline

## freqBodyAccelerometerJerk-std()-Z {#freqbodyaccelerometerjerk-std-z}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10290        |
+-------------------------+--------------+
| Median                  | -0.96        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.59 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-56-freqBodyAccelerometerJerk-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5550L, 311L, 824L, 947L, 959L, 732L, 
459L, 222L, 121L, 84L, 55L, 19L, 10L, 4L, 0L, 0L, 0L, 0L, 1L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometerJerk-std()-Z")
```

\emini

\fullline

## freqBodyAccelerometerJerk-meanFreq()-X {#freqbodyaccelerometerjerk-meanfreq-x}

\bminione

+-------------------------+-----------+
| Feature                 | Result    |
+:========================+==========:+
| Variable type           | numeric   |
+-------------------------+-----------+
| Number of missing obs.  | 0 (0 %)   |
+-------------------------+-----------+
| Number of unique values | 10298     |
+-------------------------+-----------+
| Median                  | -0.05     |
+-------------------------+-----------+
| 1st and 3rd quartiles   | -0.3; 0.2 |
+-------------------------+-----------+
| Min. and max.           | -1; 1     |
+-------------------------+-----------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-57-freqBodyAccelerometerJerk-meanFreq()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 5L, 40L, 132L, 364L, 802L, 1200L, 
1181L, 947L, 832L, 938L, 1224L, 1269L, 890L, 356L, 71L, 29L, 
13L, 4L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyAccelerometerJerk-meanFreq()-X")
```

\emini

\fullline

## freqBodyAccelerometerJerk-meanFreq()-Y {#freqbodyaccelerometerjerk-meanfreq-y}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10299       |
+-------------------------+-------------+
| Median                  | -0.24       |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.43; 0.01 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-58-freqBodyAccelerometerJerk-meanFreq()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(7L, 40L, 154L, 465L, 957L, 1370L, 1386L, 
1177L, 1027L, 1051L, 1114L, 887L, 437L, 161L, 48L, 11L, 4L, 0L, 
0L, 3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometerJerk-meanFreq()-Y")
```

\emini

\fullline

## freqBodyAccelerometerJerk-meanFreq()-Z {#freqbodyaccelerometerjerk-meanfreq-z}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10298       |
+-------------------------+-------------+
| Median                  | -0.1        |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.33; 0.09 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-59-freqBodyAccelerometerJerk-meanFreq()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(10L, 44L, 103L, 266L, 579L, 881L, 1048L, 
1120L, 1123L, 1199L, 1484L, 1254L, 777L, 294L, 93L, 19L, 2L, 
0L, 2L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyAccelerometerJerk-meanFreq()-Z")
```

\emini

\fullline

## freqBodyGyroscope-mean()-X {#freqbodygyroscope-mean-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10297        |
+-------------------------+--------------+
| Median                  | -0.89        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.38 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-60-freqBodyGyroscope-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5093L, 374L, 135L, 282L, 616L, 1060L, 
937L, 721L, 452L, 288L, 154L, 77L, 45L, 23L, 14L, 9L, 8L, 6L, 
2L, 3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyGyroscope-mean()-X")
```

\emini

\fullline

## freqBodyGyroscope-mean()-Y {#freqbodygyroscope-mean-y}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10296        |
+-------------------------+--------------+
| Median                  | -0.92        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.47 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-61-freqBodyGyroscope-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5303L, 244L, 206L, 792L, 968L, 780L, 
667L, 457L, 299L, 211L, 147L, 81L, 61L, 27L, 19L, 13L, 15L, 5L, 
1L, 3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyGyroscope-mean()-Y")
```

\emini

\fullline

## freqBodyGyroscope-mean()-Z {#freqbodygyroscope-mean-z}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10297        |
+-------------------------+--------------+
| Median                  | -0.89        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.32 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-62-freqBodyGyroscope-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5051L, 468L, 88L, 165L, 381L, 776L, 
1006L, 833L, 627L, 397L, 204L, 117L, 62L, 49L, 34L, 21L, 11L, 
3L, 4L, 2L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyGyroscope-mean()-Z")
```

\emini

\fullline

## freqBodyGyroscope-std()-X {#freqbodygyroscope-std-x}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10297        |
+-------------------------+--------------+
| Median                  | -0.91        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.52 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-63-freqBodyGyroscope-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5191L, 320L, 385L, 979L, 1082L, 852L, 
608L, 413L, 233L, 125L, 61L, 24L, 10L, 7L, 6L, 1L, 0L, 0L, 1L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyGyroscope-std()-X")
```

\emini

\fullline

## freqBodyGyroscope-std()-Y {#freqbodygyroscope-std-y}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10293        |
+-------------------------+--------------+
| Median                  | -0.91        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.44 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-64-freqBodyGyroscope-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5202L, 328L, 119L, 457L, 1036L, 896L, 
624L, 386L, 347L, 245L, 208L, 192L, 102L, 66L, 27L, 25L, 12L, 
17L, 8L, 2L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyGyroscope-std()-Y")
```

\emini

\fullline

## freqBodyGyroscope-std()-Z {#freqbodygyroscope-std-z}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10295        |
+-------------------------+--------------+
| Median                  | -0.89        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.42 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-65-freqBodyGyroscope-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5080L, 439L, 179L, 390L, 727L, 1094L, 
945L, 668L, 340L, 156L, 102L, 59L, 32L, 27L, 19L, 18L, 10L, 6L, 
3L, 5L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyGyroscope-std()-Z")
```

\emini

\fullline

## freqBodyGyroscope-meanFreq()-X {#freqbodygyroscope-meanfreq-x}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10298       |
+-------------------------+-------------+
| Median                  | -0.1        |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.27; 0.07 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-66-freqBodyGyroscope-meanFreq()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(9L, 21L, 71L, 179L, 354L, 650L, 957L, 
1280L, 1604L, 1625L, 1358L, 991L, 629L, 303L, 168L, 69L, 20L, 
5L, 3L, 3L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyGyroscope-meanFreq()-X")
```

\emini

\fullline

## freqBodyGyroscope-meanFreq()-Y {#freqbodygyroscope-meanfreq-y}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10299       |
+-------------------------+-------------+
| Median                  | -0.17       |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.36; 0.01 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-67-freqBodyGyroscope-meanFreq()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(26L, 86L, 193L, 315L, 601L, 929L, 1196L, 
1413L, 1430L, 1361L, 1132L, 761L, 450L, 235L, 93L, 48L, 24L, 
3L, 0L, 3L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyGyroscope-meanFreq()-Y")
```

\emini

\fullline

## freqBodyGyroscope-meanFreq()-Z {#freqbodygyroscope-meanfreq-z}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10299       |
+-------------------------+-------------+
| Median                  | -0.05       |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.23; 0.12 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-68-freqBodyGyroscope-meanFreq()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(7L, 20L, 48L, 112L, 270L, 489L, 836L, 
1194L, 1423L, 1657L, 1412L, 1062L, 754L, 511L, 287L, 151L, 41L, 
13L, 9L, 3L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyGyroscope-meanFreq()-Z")
```

\emini

\fullline

## freqBodyAccelerometerMagnitude-mean() {#freqbodyaccelerometermagnitude-mean}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10296        |
+-------------------------+--------------+
| Median                  | -0.88        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.22 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-69-freqBodyAccelerometerMagnitude-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5013L, 352L, 121L, 82L, 187L, 617L, 
790L, 696L, 647L, 550L, 376L, 318L, 250L, 129L, 90L, 39L, 20L, 
11L, 6L, 5L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyAccelerometerMagnitude-mean()")
```

\emini

\fullline

## freqBodyAccelerometerMagnitude-std() {#freqbodyaccelerometermagnitude-std}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10298        |
+-------------------------+--------------+
| Median                  | -0.85        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.38 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-70-freqBodyAccelerometerMagnitude-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4916L, 388L, 130L, 322L, 703L, 1060L, 
944L, 546L, 401L, 381L, 277L, 158L, 53L, 11L, 4L, 2L, 1L, 0L, 
1L, 1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometerMagnitude-std()")
```

\emini

\fullline

## freqBodyAccelerometerMagnitude-meanFreq() {#freqbodyaccelerometermagnitude-meanfreq}

\bminione

+-------------------------+------------+
| Feature                 | Result     |
+:========================+===========:+
| Variable type           | numeric    |
+-------------------------+------------+
| Number of missing obs.  | 0 (0 %)    |
+-------------------------+------------+
| Number of unique values | 10299      |
+-------------------------+------------+
| Median                  | 0.07       |
+-------------------------+------------+
| 1st and 3rd quartiles   | -0.1; 0.24 |
+-------------------------+------------+
| Min. and max.           | -1; 1      |
+-------------------------+------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-71-freqBodyAccelerometerMagnitude-meanFreq()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4L, 5L, 13L, 36L, 96L, 202L, 373L, 684L, 
1120L, 1453L, 1645L, 1478L, 1231L, 779L, 544L, 341L, 198L, 72L, 
18L, 7L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometerMagnitude-meanFreq()")
```

\emini

\fullline

## freqBodyAccelerometerJerkMagnitude-mean() {#freqbodyaccelerometerjerkmagnitude-mean}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10290        |
+-------------------------+--------------+
| Median                  | -0.93        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.26 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-72-freqBodyAccelerometerJerkMagnitude-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5362L, 212L, 66L, 109L, 304L, 603L, 
784L, 686L, 612L, 575L, 420L, 249L, 141L, 75L, 52L, 17L, 21L, 
5L, 3L, 3L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyAccelerometerJerkMagnitude-mean()")
```

\emini

\fullline

## freqBodyAccelerometerJerkMagnitude-std() {#freqbodyaccelerometerjerkmagnitude-std}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10296        |
+-------------------------+--------------+
| Median                  | -0.93        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.31 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-73-freqBodyAccelerometerJerkMagnitude-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5334L, 231L, 97L, 160L, 507L, 781L, 
653L, 604L, 580L, 490L, 378L, 225L, 134L, 66L, 30L, 16L, 3L, 
6L, 3L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyAccelerometerJerkMagnitude-std()")
```

\emini

\fullline

## freqBodyAccelerometerJerkMagnitude-meanFreq() {#freqbodyaccelerometerjerkmagnitude-meanfreq}

\bminione

+-------------------------+---------+
| Feature                 | Result  |
+:========================+========:+
| Variable type           | numeric |
+-------------------------+---------+
| Number of missing obs.  | 0 (0 %) |
+-------------------------+---------+
| Number of unique values | 10299   |
+-------------------------+---------+
| Median                  | 0.16    |
+-------------------------+---------+
| 1st and 3rd quartiles   | 0; 0.36 |
+-------------------------+---------+
| Min. and max.           | -1; 1   |
+-------------------------+---------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-74-freqBodyAccelerometerJerkMagnitude-meanFreq()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 0L, 4L, 14L, 32L, 64L, 129L, 412L, 
763L, 1211L, 1530L, 1542L, 1348L, 1156L, 991L, 619L, 357L, 105L, 
19L, 2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyAccelerometerJerkMagnitude-meanFreq()")
```

\emini

\fullline

## freqBodyGyroscopeMagnitude-mean() {#freqbodygyroscopemagnitude-mean}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10297        |
+-------------------------+--------------+
| Median                  | -0.88        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.45 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-75-freqBodyGyroscopeMagnitude-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4936L, 521L, 179L, 592L, 986L, 1043L, 
769L, 491L, 308L, 191L, 115L, 65L, 36L, 26L, 20L, 11L, 5L, 3L, 
1L, 1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyGyroscopeMagnitude-mean()")
```

\emini

\fullline

## freqBodyGyroscopeMagnitude-std() {#freqbodygyroscopemagnitude-std}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10296        |
+-------------------------+--------------+
| Median                  | -0.83        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.98; -0.47 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-76-freqBodyGyroscopeMagnitude-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4638L, 634L, 400L, 755L, 1029L, 878L, 
736L, 541L, 289L, 160L, 84L, 73L, 30L, 18L, 21L, 9L, 2L, 0L, 
0L, 2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyGyroscopeMagnitude-std()")
```

\emini

\fullline

## freqBodyGyroscopeMagnitude-meanFreq() {#freqbodygyroscopemagnitude-meanfreq}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10299       |
+-------------------------+-------------+
| Median                  | -0.05       |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.23; 0.15 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-77-freqBodyGyroscopeMagnitude-meanFreq()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(9L, 25L, 46L, 119L, 264L, 497L, 828L, 
1291L, 1415L, 1385L, 1240L, 1087L, 871L, 572L, 376L, 177L, 56L, 
19L, 15L, 7L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "freqBodyGyroscopeMagnitude-meanFreq()")
```

\emini

\fullline

## freqBodyGyroscopeJerkMagnitude-mean() {#freqbodygyroscopejerkmagnitude-mean}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10293        |
+-------------------------+--------------+
| Median                  | -0.95        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.61 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-78-freqBodyGyroscopeJerkMagnitude-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5446L, 348L, 874L, 1191L, 971L, 567L, 
318L, 188L, 130L, 103L, 64L, 36L, 32L, 11L, 9L, 3L, 6L, 0L, 1L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyGyroscopeJerkMagnitude-mean()")
```

\emini

\fullline

## freqBodyGyroscopeJerkMagnitude-std() {#freqbodygyroscopejerkmagnitude-std}

\bminione

+-------------------------+--------------+
| Feature                 | Result       |
+:========================+=============:+
| Variable type           | numeric      |
+-------------------------+--------------+
| Number of missing obs.  | 0 (0 %)      |
+-------------------------+--------------+
| Number of unique values | 10292        |
+-------------------------+--------------+
| Median                  | -0.94        |
+-------------------------+--------------+
| 1st and 3rd quartiles   | -0.99; -0.64 |
+-------------------------+--------------+
| Min. and max.           | -1; 1        |
+-------------------------+--------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-79-freqBodyGyroscopeJerkMagnitude-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5414L, 579L, 1104L, 1100L, 791L, 510L, 
298L, 160L, 114L, 74L, 50L, 35L, 29L, 16L, 11L, 5L, 4L, 2L, 2L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyGyroscopeJerkMagnitude-std()")
```

\emini

\fullline

## freqBodyGyroscopeJerkMagnitude-meanFreq() {#freqbodygyroscopejerkmagnitude-meanfreq}

\bminione

+-------------------------+-------------+
| Feature                 | Result      |
+:========================+============:+
| Variable type           | numeric     |
+-------------------------+-------------+
| Number of missing obs.  | 0 (0 %)     |
+-------------------------+-------------+
| Number of unique values | 10299       |
+-------------------------+-------------+
| Median                  | 0.14        |
+-------------------------+-------------+
| 1st and 3rd quartiles   | -0.02; 0.29 |
+-------------------------+-------------+
| Min. and max.           | -1; 1       |
+-------------------------+-------------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-80-freqBodyGyroscopeJerkMagnitude-meanFreq()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(3L, 3L, 10L, 31L, 95L, 141L, 257L, 390L, 
738L, 1197L, 1646L, 1784L, 1582L, 1134L, 714L, 379L, 131L, 50L, 
11L, 3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "freqBodyGyroscopeJerkMagnitude-meanFreq()")
```

\emini

\fullline

## subject

\bminione

+-------------------------+---------+
| Feature                 | Result  |
+:========================+========:+
| Variable type           | integer |
+-------------------------+---------+
| Number of missing obs.  | 0 (0 %) |
+-------------------------+---------+
| Number of unique values | 30      |
+-------------------------+---------+
| Median                  | 17      |
+-------------------------+---------+
| 1st and 3rd quartiles   | 9; 24   |
+-------------------------+---------+
| Min. and max.           | 1; 30   |
+-------------------------+---------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-81-subject', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28), xmax = c(2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28, 30), ymin = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(649L, 658L, 627L, 589L, 
582L, 636L, 650L, 694L, 732L, 714L, 729L, 753L, 801L, 758L, 727L
)), class = "data.frame", row.names = c(NA, -15L)), vnam = "subject")
```

\emini

\fullline

## activity

\bminione

+-------------------------+-----------+
| Feature                 | Result    |
+:========================+==========:+
| Variable type           | character |
+-------------------------+-----------+
| Number of missing obs.  | 0 (0 %)   |
+-------------------------+-----------+
| Number of unique values | 6         |
+-------------------------+-----------+
| Mode                    | "LAYING"  |
+-------------------------+-----------+

```{=tex}
\emini
\bminitwo
```
```{r 'Var-82-activity', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:6, .Label = c("LAYING", 
"SITTING", "STANDING", "WALKING", "WALKING_DOWNSTAIRS", "WALKING_UPSTAIRS"
), class = "factor"), y = c(1944L, 1777L, 1906L, 1722L, 1406L, 
1544L)), class = "data.frame", row.names = c(NA, -6L)), vnam = "activity")
```

\emini

-   Observed factor levels: "LAYING", "SITTING", "STANDING", "WALKING", "WALKING_DOWNSTAIRS", "WALKING_UPSTAIRS".

\fullline

Report generation information:

-   Report creation date: Wed Jun 30 2021

-   dataMaid v1.4.0 [Pkg: 2019-12-10 from CRAN (R 4.1.0)]

-   R version 4.1.0 (2021-05-18).

-   Platform: x86_64-w64-mingw32/x64 (64-bit)(Windows 10 x64 (build 19042)).

-   Function call: `dataMaid::makeDataReport(data = tidydata, mode = c("summarize",  "visualize", "check"), smartNum = FALSE, file = "codebook_tidydata.Rmd",      checks = list(character = "showAllFactorLevels", factor = "showAllFactorLevels",          labelled = "showAllFactorLevels", haven_labelled = "showAllFactorLevels",          numeric = NULL, integer = NULL, logical = NULL, Date = NULL),      listChecks = FALSE, maxProbVals = Inf, codebook = TRUE, reportTitle = "Codebook for tidydata")`
